Results_setup

### 2020-04-09 src/Result_Setup.Rmd
copying code chuncks for DMC1

@@

>>>>

# DMC1 Results

main table (DMC1.mean.table), t.tests  , ratios

set up, t.tests, correlations

```{r DMC1.setup, echo=FALSE}
#load DMC1 csv
#DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)
DMC1.DF <- read.csv("~./MLH1repo/data/DMC1newJuviQuant.csv", header = TRUE)

DMC1.DF$fileName <- DMC1.DF$Original.Name
DMC1.DF <- add_mouse(DMC1.DF)
DMC1.DF <- add_strain(DMC1.DF)
DMC1.DF <- add_category(DMC1.DF)
DMC1.DF <- add_subsp(DMC1.DF)
DMC1.DF <- DMC1.DF[DMC1.DF$stage != "P",]

#make DMC1 table
DMC1.mean.obs.L <- ddply(.data=DMC1.DF[DMC1.DF$stage == "L",],
                 .(category),
                 summarize,

                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.L$stage <- "L"

DMC1.mean.obs.Z <- ddply(.data=DMC1.DF[DMC1.DF$stage == "Z",],
                 .(category),
                 summarize, 
                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.Z$stage <- "Z"

DMC1.mean.table <- rbind(DMC1.mean.obs.L,DMC1.mean.obs.Z)

#write.table(DMC1.mean.table, "~./MLH1repo/DMC1.mean.table.csv", sep=",",
#            row.names = FALSE)

DMC1.DF$rec_group <- ifelse(grepl("WSB", DMC1.DF$strain), "Low",
                          ifelse(grepl("G",DMC1.DF$strain), "Low",

              ifelse(grepl("KAZ", DMC1.DF$strain), "Low",
            ifelse(grepl("PWD", DMC1.DF$strain), "High",
               ifelse(grepl("MSM", DMC1.DF$strain), "High","")))))

#make category averages from AP_mouse_table.HQ
mean.MLH1.obs <- ddply(.data=AP_mouse_table.HQ,
                 .(category),
                 summarize, 
                 mean.MLH1 = mean(mean_co),
                 var.MLH1 = var(mean_co)
)

DMC1.target.strains <- subset(mean.MLH1.obs, category == "G male" |
                   category == "WSB male" |
                     category == "KAZ male" |
                  category == "MSM male" |
                    category == "PWD male")
#attach this mini DF to the DMC1 data

```{r DMC1_t.tests, echo=FALSE, warning=FALSE}
#2. t-tests for the DMC1 counts 
#need to account for sample sizes when comparing t.tests (KAZ and G don't have equal across )
#best case scnario -- more microscoping to get ~20 cells for each stage by strain combo

#high vs low group (L)
ttest.HighLow.L.pval <- t.test(DMC1.DF$total.count[( (DMC1.DF$stage == "L") & ( ( DMC1.DF$strain == "MSM") | (DMC1.DF$strain == "PWD") ) )  ],
               DMC1.DF$total.count[( (DMC1.DF$stage == "L") & ( ( DMC1.DF$strain == "WSB") | (DMC1.DF$strain == "G") | (DMC1.DF$strain == "KAZ") ) )]    )$p.value
# p-value =  0.002145

#high vs low group (Z)
ttest.HighLow.Z.pval <- t.test(DMC1.DF$total.count[( (DMC1.DF$stage == "Z") & ( ( DMC1.DF$strain == "MSM") | (DMC1.DF$strain == "PWD") ) )  ],
               DMC1.DF$total.count[( (DMC1.DF$stage == "Z") & ( ( DMC1.DF$strain == "WSB") | (DMC1.DF$strain == "G") | (DMC1.DF$strain == "KAZ") ) )]    )$p.value
# p-value = 0.6628

#dom vs musc (L) (2 subsp vs)
ttest.subsp.L <- t.test(DMC1.DF$total.count[(DMC1.DF$subsp == "Dom") & (DMC1.DF$stage == "L")], DMC1.DF$total.count[(DMC1.DF$subsp == "Musc") & (DMC1.DF$stage == "L")] )
# p-value = 0.003016

#dom vs musc (Z)
ttest.subsp.Z <- t.test(DMC1.DF$total.count[(DMC1.DF$subsp == "Dom") & (DMC1.DF$stage == "Z")], DMC1.DF$total.count[(DMC1.DF$subsp == "Musc") & (DMC1.DF$stage == "Z")] )
#p-value = 0.09588

#KAZ vs Dom (Z) (only 1 L cell)
ttest.KAZ.Dom.z <- t.test(DMC1.DF$total.count[(DMC1.DF$subsp == "Dom") & (DMC1.DF$stage == "Z")], 
      DMC1.DF$total.count[(DMC1.DF$strain == "KAZ") & (DMC1.DF$stage == "Z")] )

#p-value = 0.004148
#Kaz Z are higher than Dom
```

```{r DMC1.rand.calq, echo=FALSE}

DMC1.mean.obs.L$mean.count.L <- DMC1.mean.obs.L$mean.count
DMC1.mean.obs.Z$mean.count.Z <- DMC1.mean.obs.Z$mean.count

DMC1table <- merge(DMC1.mean.obs.L, DMC1.mean.obs.Z, by="category")

DMC1table.main <- merge(DMC1.target.strains, DMC1table, by="category")

MLH1.DMC1.L_cor <- cor(DMC1table.main$mean.MLH1, DMC1table.main$mean.count.L, method = c("pearson"))#MLH1.DMC1.Z_cor

MLH1.DMC1.Z_cor <- cor(DMC1table.main$mean.MLH1, DMC1table.main$mean.count.Z, method = c("pearson"))#0.2793237
```

```{r DMC1.ratios, echo=FALSE}

##RATIOS
DMC1table.main$MLH1.L_ratio <- DMC1table.main$mean.MLH1/ DMC1table.main$mean.count.L 
DMC1table.main$MLH1.Z_ratio <- DMC1table.main$mean.MLH1 / DMC1table.main$mean.count.Z

#colnames(DMC1table.main) <- c("category", "mean.MLH1", "", "", "")

#DMC1.mean.table
DMC1.mean.table.99 <- subset(DMC1table.main, select= -c(var.MLH1,  mean.count.x,  mean.count.y, stage.x, stage.y))

colnames(DMC1.mean.table.99) <- c("category","mean.MLH1","ncells.L","mean.L",
                  "ncells.Z", "mean.Z", "MLH1.L_ratio", "MLH1.Z_ratio")

WSB_DMC1.Z_CO_ratio <-   ( DMC1table.main %>% filter(category == "WSB male") )$mean.count.L / (DMC1table.main %>% filter(category == "WSB male"))$mean.MLH1

G_DMC1.Z_CO_ratio <-   ( DMC1table.main %>% filter(category == "G male") )$mean.count.L / (DMC1table.main %>% filter(category == "G male"))$mean.MLH1

MSM_DMC1.Z_CO_ratio <- ( DMC1table.main %>% filter(category == "MSM male") )$mean.count.L / (DMC1table.main %>% filter(category == "MSM male"))$mean.MLH1

PWD_DMC1.Z_CO_ratio <-( DMC1table.main %>% filter(category == "PWD male") )$mean.count.L / (DMC1table.main %>% filter(category == "PWD male"))$mean.MLH1

DMC1table.main$category <- factor(DMC1table.main$category, levels = c("WSB male","G male","KAZ male",               "PWD male","MSM male"), ordered = TRUE )

DMC1table.main <- DMC1table.main[order(DMC1table.main$category),]

kable(head(DMC1table.main),  caption = "Table X. DMC1 foci counts per cell summary")

DMC1.Lratio_t.test <- t.test(  (DMC1table.main %>% filter(  ( category == "G male" | category == "WSB male" | category == "KAZ male" ) ) )$MLH1.L_ratio, 
                (DMC1table.main %>% filter(  ( category == "PWD male" | category == "MSM male") ) )$MLH1.L_ratio        )

DMC1.Zratio_t.test <- t.test(  (DMC1table.main %>% filter(  ( category == "G male" | category == "WSB male" | category == "KAZ male" ) ) )$MLH1.Z_ratio, 
                (DMC1table.main %>% filter(  ( category == "PWD male" | category == "MSM male") ) )$MLH1.Z_ratio        )

@@

```{r Save.File, echo=FALSE}
